---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

```{r init, echo=FALSE}
set.seed(0)

```

# comparer

[![Travis-CI Build Status](https://travis-ci.org/CollinErickson/comparer.svg?branch=master)](https://travis-ci.org/CollinErickson/comparer)

The goal of comparer is to make it easy to compare the results of different code
chunks that are trying to do the same thing.
The R package `microbenchmark` is great for comparing the speed of code,
but there's no way to compare their ouput to see which is more accurate.

## Installation

You can install comparer from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("CollinErickson/comparer")
```

## Example

The main function of this package is `mbc`, for "model benchmark compare".
It is designed to be similar to the package `microbenchmark`,
allow for fast comparisons except including the output/accuracy of the
code evaluated instead of just timing.


Suppose you want to see how the mean and median of a sample of 100 randomly
generated data points from an exponential compare.
Then, as demonstrated below, you can use the function `mbc`,
with the functions mean and median, and then `input=rexp(100)`.
It outputs the run times of each, and then the results from the
five trials, where five is the default setting for `times`.
The run times aren't useful because they are all fast.
For more precise timing (<0.01 seconds), you should use `microbenchmark`.
The trials all have the same output since there is no randomness,
the same data is used for each trial.
The "Output summary" shows that the mean is near 1, while the median
is near 0.6.

```{r mbc_example}
## basic example code
library(comparer)
mbc(mean, median, input=rexp(100))
```

To get the data to be generated for each trial,
use the `inputi` argument to set a variable that the 
functions call.
The arguments `mean(x)` and `median(x)` are captured as expressions,
as is `{x=rexp(100)}` for `inputi`. Note that you must put brackets around
the value of `inputi` if it is an expression or it will give an error.
You can see that the values are now different for each trial.

```{r mbc_example2}
## Regenerate the data each time.
mbc(mean(x), median(x), inputi={x=rexp(100)})
```
